GSE158420: RNA expression downsampling

### 2024-09-13 analysis/GSE158420_rna.Rmd
bugfix

>>>>

# output some data for the paper
head(fores[[1]])
message("FORA TP")lapply(fores,function(mx) { summary( mx[,2] ) } )
message("FGSEA TP") ; lapply(fgres,function(mx) { summary( mx[,2] ) } )
message("FORA FP") ; lapply(fores,function(mx) { summary( mx[,3] ) } )
message("FGSEA FP") ; lapply(fores,function(mx) { summary( mx[,3] ) } )
message("FORA FP proportion") ; lapply(fo1,summary)
message("FGSEA FP proportion") ; lapply(fg1,summary)
